---
title: "Penguins Plots"
author: "Yan"
date: "2023-07-26"
output: html_document
---

## Setting up my environment

Notes: setting up my R environment by loading the 'tidyverse' and 'palmerpenguins' packages

```{r loading packages, message=TRUE, warning=FALSE}
library(tidyverse)
library(palmerpenguins)
```

## Summary penguins data

```{r warning=FALSE, paged.print=TRUE}
summary(penguins)
```

## Visualizations

Here we will go through a series of visualizations \### Flipper and body mass in purple Here we plot flipper length against body mass

```{r warning=FALSE}
ggplot(data=penguins,aes(x=flipper_length_mm,y=body_mass_g))+
  geom_point(color="purple")
```

### Flipper and body mass by species

Here we plot flipper length against body mass and look at the breakdown by species

```{r warning=FALSE}
ggplot(data=penguins,aes(x=flipper_length_mm,y=body_mass_g))+
  geom_point(aes(shape=species))
```

### Flipper and body mass by species and sex

Here, we plot flipper length against body mass and look at the breakdown by species and sex

```{r warning=FALSE}
ggplot(data=penguins,aes(x=flipper_length_mm,y=body_mass_g))+
  geom_point(aes(color=species,
                 shape=species)) +
  facet_wrap(~sex)
```
